Co-methylation

### 2014-12-23 Rmarkdown/comethylation.Rmd
Still need to think about NIL >= 0 co-methylation results

These plots appear to show that there is a dramatic increase in within-fragment co-methylation at precisely these $IPD$s for paired-end samples from the Lister dataset. However, I am very skeptical as to the biological relevance of these results.

@@

As discussed in Section \ref{sec:m-bias}, the incomplete removal of M-bias is a real problem for reads that have undergone pre-trimming because this destroys the relationship between read-position and sequencing cycle. __FIGURE__ shows that there is considerable variation in the read lengths of the _ADS_ sample, indicative of aggressive pre-trimming of these reads (__TODO: Histogram of read lengths__).

@@

__TODO: Summarise the M-bias issue__

>>>>

__TODO: Re-write everything between @@@@@. I'm really not yet sure if this result is biology or an artefact. My instinct says artefact but I haven't yet been able to prove this either way to my satisfaction__
@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
These plots appear to show that there is a dramatic increase in within-fragment co-methylation at precisely these $IPD$s for paired-end samples from the Lister dataset. However, I am very skeptical as to the biological relevance of these results.

@@

As discussed in Section \ref{sec:m-bias}, the incomplete removal of M-bias is a real problem for reads that have undergone pre-trimming because this destroys the relationship between read-position and sequencing cycle. __FIGURE__ shows that while there is considerable variation in the read lengths of the _ADS_ sample, which is indicative of aggressive pre-trimming of these reads, most reads are full length or close to it (__TODO: Histogram of read lengths__).

@@

__TODO: Summarise the M-bias issue__
@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@@
